    \begin{itemize}
        \item \textbf{OuYang, RuiKang}, Yu, Hanlin, Ai, Xinyue, He, Yutong, Boffi, Nicholas Matthew, Ravikumar, Pradeep, Hernández-Lobato, José Miguel, Simchowitz, Max, Miller, Benjamin Kurt, and Chehab, Omar (2026). {\color{teal}Few-Step Boltzmann Generators via Scalable Likelihood Flow Maps}. \textit{SPIGM@ICML}.
        \item Yu, Hanlin, \textbf{OuYang, RuiKang}, Kaushik, Partha, Klami, Arto, Gutmann, Michael U., and Chehab, Omar (2026). {\color{teal}Learning Energy-Based Models from Stochastic Interpolants using Spatiotemporal Differences}. \textit{Preprint}.
        \item \textbf{OuYang, RuiKang*}, Grenioux, Louis*, and Hernández-Lobato, José Miguel (2026). {\color{teal}A Diffusive Classification Loss for Learning Energy-based Generative Models}. \textit{ICML}.
        \item Yu, James Boran, \textbf{OuYang, RuiKang}, Horwood, Julien, and Hernández-Lobato, José Miguel (2026). {\color{teal}Stochastic Interpolants in Hilbert Spaces}. \textit{Preprint}.
        \item \textbf{OuYang, RuiKang*}, Rissanen, Severi*, He, Jiajun, Chen, Wenlin, Heinonen, Markus, Solin, Arno, and Hernández-Lobato, José Miguel (2025). {\color{teal}Progressive Tempering Sampler with Diffusion}. \textit{ICML}.
        \item He, Jiajun*, Du, Yuanqi*, Vargas, Francisco, Zhang, Dinghuai, Padhy, Shreyas, \textbf{OuYang, RuiKang}, Gomes, Carla, and Hernández-Lobato, José Miguel (2025). {\color{teal}No Trick, No Treat: Pursuits and Challenges Towards Simulation-free Training of Neural Samplers}. \textit{FPI@ICLR}.
        \item \textbf{OuYang, RuiKang*}, Qiang, Bo*, and Hernández-Lobato, José Miguel (2025). {\color{teal}BNEM: A Boltzmann Sampler Based on Bootstrapped Noised Energy Matching}. \textit{TMLR}.
        \item \textbf{OuYang, RuiKang} (2024). {\color{teal}Energy-Based Diffusion Neural Sampler for Boltzmann Densities}. \textit{MPhil Thesis}.
        \item \textbf{OuYang, RuiKang}, Elliott, Andrew, Limnios, Stratis, Cucuringu, Mihai, and Reinert, Gesine (2023). {\color{teal}L2G2G: A Scalable Local-to-Global Network Embedding with Graph Autoencoders}. \textit{CNA}.
    \end{itemize}
